\newpage
\section{Contributions}

\subsection*{Sigurdur Haukur Birgisson}

\begin{itemize}
    \item ML pipeline foundation: triplet mining, online triplet loss, and k-fold training.
    \item Data pipeline: preprocessing filters, windowing, and standardization.
    \item Model architectures: LSTM and Transformer implementations.
    \item Backend/frontend integration: FastAPI routes, web UI, and model inference.
    \item DevOps: Docker containerization and Hugging Face integration.
\end{itemize}

\subsection*{Peter Meeus}

\begin{itemize}
    \item K-fold cross-validation implementation.
    \item Evaluation metrics: FAR, FRR, and EER computation for unseen participants.
    \item Model parameter tuning and finetuning workflow.
    \item CosFace loss integration, in collaboration with Tijje.
    \item Training visualization and loss/embedding analysis.
    \item Dataset handling fixes and preprocessing optimizations.
    \item DevOps: pre-commit hooks, code formatting, and dependency management.
\end{itemize}

\subsection*{Efe}

\begin{itemize}
    \item Initial FastAPI endpoint design and setup.
    \item Template system and HTML frontend pages.
    \item API webpage and user interface development.
    \item Feature separation: model pages, user enrollment, and classification logic.
    \item API testing framework.
    \item Filter experimentation and visualization.
\end{itemize}

\subsection*{Tijje}

\begin{itemize}
    \item Custom linear layer for CosFace loss.
    \item CosFace loss function implementation and integration.
    \item Alternative loss function support alongside triplet loss.
    \item Model parameter tuning code and setup support.
\end{itemize}
