\section{Validation Evidence}

The Transformer model achieves a validation equal error rate (EER) of 7.68\%. In contrast, a random baseline would yield an EER of 50\%, corresponding to randomly accepting or rejecting embeddings. This substantial difference demonstrates that the model significantly outperforms random guessing on the validation data $(7.68\% \ll 50\%)$. Since this is an open-set verification task (distinguishing genuine gait from all other gaits) rather than multiclass classification, EER is the appropriate metric to report rather than accuracy. Accuracy is misleading in biometric verification because it conflates false positives and false negatives. False positives and false negatives have asymmetric costs in practice, a false positive (accepting an impostor) is typically more costly than a false negative (rejecting a legitimate user). EER reports the error rate at the threshold where false positives and false negatives are equal, providing a more meaningful measure of model performance in this context.

An EER of 7.68\% translates to approximately 8 errors per 100 authentication requests, distributed as a mix of false positives and false negatives. While it is slightly high, we can adjust the decision threshold to trade off between false positives and false negatives based on the application's requirements. For example, if we prioritize security and want to minimize false positives, we can raise the threshold, which would reduce the false acceptance rate at the cost of increasing the false rejection rate. Conversely, if we want to minimize inconvenience for legitimate users, we can lower the threshold, which would reduce false rejections but increase false acceptances. For this project, kept the threshold such that the false positive and false negative rates are balanced.