\section{Relation to Grading Specifications}
% \begin{itemize}
%     \item How does your project meet the minimum requirements?
%     \item What is your argument for novelty?
%     \item What is your preprocessing plan?
%     \item Which hyperparameters might you optimize?
%     \item Which things do you intend to do to boost your grade?
%     \item Which things do you intend to do to further boost your grade?
% \end{itemize}

% Minimum requirements:
% - Preprocessing
% - Cross-validation
% - Hyperparameter optimization
% - Evaluation of over/underfitting with regularization
% - Novelty
% - Organised and reproducible github repo with commit history

Our preprocessing plan is to start with the segmented windows, check for sensor artifacts and outliers, normalize each channel using training-data statistics, and then prepare either raw windows or engineered features depending on the model. For cross-validation, we will use subject-level splits so that data from the same person does not appear in both training and testing, which better measures generalization to new users. For optimization, we will tune the main hyperparameters of each model, such as learning rate, dropout, regularization strength, and model-specific architecture settings, using validation performance. To evaluate overfitting, we will compare training and validation performance and use regularization methods such as dropout, L2 regularization, and early stopping when needed. 

\newpage
We also see our novelty coming from the in the real-world setting of gait-based owner verification on phone sensor data, especially because we want the model to generalize to unseen people rather than only recognize users it has already seen. In addition, we aim to keep the model lightweight enough for possible smartphone deployment. The project should also satisfies the reproducibility requirements. We have maintained a structured GitHub repository from the start, used feature branches, written clear commit messages, and kept notes and code organized so the workflow can be followed and reproduced.