\section{Risk Assessment}
% \begin{itemize}
%     \item What are the potential risks related to your project?
%     \item What issues may you expect during development?
%     \item How would you circumvent this?
%     \item How likely is this project to be successful?
%     \item What are societal or user risks when your model is deployed publicly?
%     \item \textbf{Required:} At least one threat to your project development and an estimate of success.
%     \item \textbf{Required:} A consideration of possible risks of having your model deployed.
% \end{itemize}

Some potential risks related to project development include data leakage across training and test sets, over-complexity of the transformer models for the task, a trade-off between model size and accuracy, and the need to learn new techniques for model compression and deployment.

During development, we may encounter issues on several fronts. As transformer models are often large and computationally expensive, we may end up with an overly-complicated model that is lenient to overfitting. We may also face challenges in handling live streaming sensor data, which is both technically demanding and sensitive in nature. Additionally, deployment constraints may require us to learn techniques specific to this use case, such as mobile development.

To mitigate these risks, we adopt several strategies. To prevent data leakage, as mentioned in previous sections, we will split the data by subject so that no sensor data from a test subject appears in training. To address model complexity, we will start with a smaller transformer architecture and only increase complexity if necessary, using the baseline model as a reference. We will also apply regularization techniques such as dropout and early stopping to prevent overfitting.

To prepare for deployment challenges early, we plan to study projects such as the web fake beer drinking app to understand how live streaming sensor data is handled. Finally, to minimize privacy risks from live data, we would prefer to keep the system on-device rather than stream sensor data to a server, thereby reducing the risk of data breaches and privacy violations.

The project is likely to be successful in terms of model accuracy, since the task has already been shown to be feasible with high accuracy. What is less certain is how viable the approach will be once compression and deployment constraints are introduced.

The main societal risk is misuse: The system could be used to detect, follow, or identify someone through their embedding, which would effectively leak biometric information. There are also user risks because this system would serve as an added security layer, and users might blame the model if it fails in a sensitive situation. In a real deployment, the model would need to achieve a very high level of reliability before it could be trusted.

\newpage
